\documentclass[a4paper,12pt]{book}
\usepackage{enumitem}
\usepackage[utf8x]{inputenc}
%\usepackage{pifont} % ding
%\DeclareUnicodeCharacter {9320}{⑨}
% http://tex.stackexchange.com/questions/73560/error-unicode-char-u8%CF%86-not-set-up-for-use-with-latex
%
% Circled numbers
% http://tex.stackexchange.com/questions/7032/good-way-to-make-textcircled-numbers
% http://tex.stackexchange.com/questions/15334/getting-numbers-to-appear-in-circles
% I went with this in the end:
\newcommand{\maru}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
\newcommand{\vaultnine}{Vault \maru{9}}



\begin{document}
\frontmatter


\title{Fallout Gensokyo}
\author{Anonymous Fairy}
\date{2008}
\maketitle

% It's huge lol
% \tableofcontents

\chapter{Preface}

This isn't mine, I'm just typesetting and editing.

\begin{quote}
\emph{-- Furinkan}
\end{quote}

\mainmatter

\chapter{Introduction}

\begin{quote}
\emph{I don't want to set the world on fire;\\
I just want to start a flame in your heart.}
\end{quote}


War. War never changes. At the dawn of civilization, when our ancestors finally discovered themselves alone in this world, without predator or rival, they became faced with a quandary. For what now would they do with that which had ensured their survival in the wild, the ability to fashion weapons from their environment, as natural for them to use as the owl its talons and the wolf its fangs? So, with no other target, they would turn their spears on each other. At all stages of history, we can define progress of humanity not in the development of the sciences, medicine, arts, or culture, but by the ever increasing capacity to kill. Though the will to survive was itself not lost, mankind would develop ever an ever growing lexicon of terms that could be used to separate themselves from the other humans more deserving of death -- tribe, nation, class, race, creed. In the year 2077, in the ultimate culmination of arbitrary justifications for violent conflict, the humans of Earth, and the Lunarians, a label given to humans of her moon, Luna, would declare war on each other over a single flag, planted unassumingly over a century earlier. It is not agreed upon by Wasteland scholars who struck first, but what is known is that that retaliation on either side was total. Thus the Earth and her moon, after a momentary flash of light, were plunged into an era of unparalleled darkness.

But it was not, as some had predicted, the end of the world. Instead, the apocalypse was simply the prologue to another bloody chapter of history. Man had succeeded in destroying himself, yes, but there were yet other forces in this world ready to take up the reins of violence. Whether they were a product of mutation after the bombs fell, whether they had been bioengineered tools of war -- super-soldiers created to resist the deleterious effects of battlefield radiation -- or whether they had always existed and were just now no longer content to hang on the fringes of man's consciousness, the theories are as numerous as the forms they would take, and these meta-humans, known in the present day Gensokyo Wasteland as youkai, were all too willing to fill the gap left by humanity's destruction. Regeneration, the ability to go without food or water indefinitely, monstrous strength, and even more wondrous powers, flight and seeming magic -- like their mundane predecessors these beings would quickly learn to bend their abilities towards any who opposed them, including each other. And so\ldots war, war never changes.

Even though a portion of humanity was to escape the terrible destructive power of the bombs themselves, the widespread extinction of terrestrial life and the poisoning of the air and water had serious ramifications for even the most sheltered of communities. Early in the year 2076 C.E., in preparation for the worst, the powers of the cloistered micronation of Gensokyo, located coterminously with what was then known as the State of Japan (a provisional member to the United States of America), decided to commission the \emph{Vault-Tec} company (a wholly owned subsidiary of Yakumo Industries) to build a series of underground shelters designed to safeguard its small population. Ten years after their internment, the ``Vaults'' were due to reopen, but when their inhabitants emerged they had only the hell of the wastes to greet them.

All, except those in \vaultnine . For on the fateful day when fire rained from the sky, the giant steel door of \vaultnine{} slid closed and never reopened\ldots for over two hundred years. It was here you were born, and it is here you will die, because in \vaultnine, no one ever enters, and no one ever leaves.






\chapter{Waking up}

Tak-tak-tak-tak-tak-tak.

You’re up looking at a woman seated at a massive podium. Noise is coming somewhere to your right, outside your field vision. You cannot see much of the woman (whether this is because you’re too short or she’s too short, you cannot tell), just her face, her coordinating white & navy outfit, and the ceremonial crown atop her head. Hunched over whatever it is that she’s reading with such intensity, you see enough to note that her short green hair frames her face nicely, that her reading glasses make her blue eyes look larger than they really are, and that her crown must be glued on to not fall off at that angle. The podium is marked by the seal embossed on it, that of a blindfolded woman holding a set of scales. You recognize the symbol’s meaning immediately: You must be in a courtroom of some kind, though most of your vision is occupied by the woman and the podium, everything else is a blinding white void.

Tak-tak-tak-tak-tak-tak. The rhythmic noise continues unabated.

Her lips mouth wordlessly along with her eyes as they pour over the unseen words before her. She hasn’t yet noticed you it seems, which is just as well because you don’t have much to say, not remembering anything before the last paragraph or so of your interior monologue. If you could do anything (and it seems you cannot, critically lacking both a physical body and the capacity for locomotion) it would probably be to adjust the crown perched so-precipitously above her forehead.

Tak-tak-tak-tak-tak, ching! A pause… and anew. Tak-tak-tak-tak.

It takes a few cycles of the tapping and the ringing before the woman’s mouth stops moving and her eyes flick toward you. For a moment. Long enough to acknowledge your presence, but not long enough to acknowledge your presence as deserving of her attention.

``Komachi.'' The voice of the woman in front of you, louder than her stature would suggest.

Tak-tak-tak—. The noise stops suddenly. A red blob enters your peripheral vision.

``Boss?'' A female voice. The blob.

The woman in front of you doesn’t answer the blob immediately, just eyes it and points an odd-looking gavel at you—vaguely the shape of a geometric deltoid, emblazoned with the letters ``U.S.A.'' in a garish red, white, and blue.

``What is this?''

A pause. Incredulity, ``Come on Boss, you know what that is; it’s a soul.'' The blob continues dismissively, ``Fresh from the wastes this morning. I’ve got the paperwork all done and everything.''

There is a ripping sound, and a slightly crumpled piece of paper is shoved in the podium woman’s face, the blob apparently having sprouted an arm, crossing more clearly into you range of vision. With a glare the woman slowly takes the paper from the blob. She adjusts her glasses, scans the paper quickly, glances at you again, and places it on the podium. She makes an attempt to flatten the wrinkles out with the side of her hand, resulting in a black smear across her right palm. Fresh ink. She considers the stained hand momentarily, almost reaches for her gavel with the same hand before stopping this apparently reflexive movement, and finally satisfies herself with only closing her eyes in consternation.

``Komachi.''

``Boss?'' More meekly this time.

``How many times must I tell you? Finish the paperwork before you bring the soul before me.'' The podium woman is clearly irate. ``How long has it been here?''

``Well… I said ‘this morning’… and it’s five o’clock now, so…'' The blob trails off.

The woman massages her temples with her unstained hand. ``Komachi, what happens when you leave a soul aware and unattended for too long?.
To her credit the blob seems to be able to quickly recite the answer from memory.

``Shinigami Code, § 110, ¶ 1: A soul deceased and yet unjudged shall only be presented before the Court once its karmic transcripts have been processed and reviewed by a duly authorized officer of the Court..

``And the next paragraph?'' The podium lady impatiently raps the stick against the wood of the podium, before wincing and dropping it in realization. Now the gavel is red, white, and black.

``A soul left unattended before the Court or in transit runs the risk of gaining a precocious awareness that may adversely affect the viability of its next reincarnation. This is a violation of the soul’s right to due process..

``Right, and we’ll make sure you understand what implications this has for you and your position later. For now, you’re going to run a triplicate of this opinion on the Nemo case over to the central office..

Grumbling. Shuffling of papers. The blob disappears once again from your field of vision, and the woman in front of you (finally) turns her attention to you with a civil smile.
``Now then, since I’m fairly certain you’ve been aware enough to hear and comprehend what I’ve been saying for at least a few hours now, I will first express my sincerest apologies for the gross miscarriage of justice you have just witnessed in my courtroom. I am Sikieiki Yamaxanadu, district judge for the greater Gensokyo area. Due to the incompetence of my aide, rather than process the judgment of your soul as I would normally, I am forced to use my discretionary power as judge to expedite your reincarnation, so as to minimize further damage to your karmic record.'' The words flow so fluidly off her tongue, you have to wonder how often she is forced to recite them. ``With that said, let’s have a look at your record..
The judge assumes a more neutral expression, readjusts her reading glasses once more, and looks down at her podium for far longer than it should take to read a single one-sided sheet of paper. Muttering something to herself, she flips the sheet over and finding it blank she glances around her workplace, before looking back at you with some alarm, and begins to turn her left for aid.

``Komachi, does this say—oh, bother.'' She stops when she notices that the red blob has not yet returned. It takes a moment for her to regain her smile, this one more strained. She picks up what looks like a hand mirror (it seems the ink on her hand has dried), and holds it at an angle toward you that obscures her face entirely. After a moment she puts the mirror down. ``Good enough,'' more to herself than to you. Seemingly satisfied, she regains her authoritative air. ``Well this is a bit of non-standard procedure, but the important thing is that I am able to judge confidently that you are not yet deserving of hell or heaven and will be bound for reincarnation for at least a dozen more standard cycles. Since I can tell you are at the very least an honest soul, we’re going to speed this along by filling in the details by direct inquiry. You cannot talk, however I will be able to read your response with my mirror. Do you understand?.

Wordless assent.

She glances at her mirror. ``Good. Now I am going to ask you just a few questions that will determine the particulars of your reincarnation. By now you should have regained enough memory of your past life that you can answer truthfully..

As you note the way her eyes bore into you, you feel what may be your first emotion, anxiety. Despite your current incapacity to express any of the physical gestures that might give away a lie, you cannot help but feel that deliberate falsehood may be dangerous here.

``My first question: What is your race? As far as I can tell from your record, your current karmic rung would determine that you be reincarnated as human, half-youkai, or fairy..

\begin{verbatim}
[ ] Human 
[ ] Half-youkai 
[ ] Fairy 
[ ] <Lie> Other (specify) 
\end{verbatim}




\end{document}
